\Large \bf 6.829 Final Project: A comparison of bit-rate selection algorithms

### 2013-05-14 paper/paper.tex
some more changes
blah

% This version uses the latex2e styles, not the very ancient 2.09 stuff.
\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig,endnotes}
\begin{document}

@@

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf 6.829 Final Project: A comparison of bit-rate selection algorithms}
%for single author (just remove % characters)
\author{
{\rm Colleen Josephson}\\
MIT
\and
{\rm Pavel Panchekha}\\
MIT
% copy the following lines to add more authors
% \and
% {\rm Name}\\
%Name Institution
} % end author

@@

% Use the following at camera-ready time to suppress page numbers.
% Comment it out when you first submit the paper for review.
\thispagestyle{empty}

@@

Yeee haw.

@@

Well, it's getting boring isn't it.  This is the last subsection
before we wrap it up.

@@

>>>>

% This version uses the latex2e styles, not the very ancient 2.09 stuff.
\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{epsfig,graphicx,usenix,fullpage}

%\usepackage{endnotes}
\begin{document}

@@

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf 6.829 Final Project: A comparison of bit-rate selection algorithms}
%for single author (just remove % characters)
\author{
{\rm Colleen Josephson\footnote{Supported in part by Lindt Chocolatier.}}\\
MIT
\and
{\rm Pavel Panchekha}\\
MIT
% copy the following lines to add more authors
% \and
% {\rm Name}\\
%Name Institution
} % end author

@@

% Use the following at camera-ready time to suppress page numbers.
% Comment it out when you first submit the paper for review.
%\thispagestyle{empty}

@@

Yeee haw.
\begin{figure}[htb]
  \hspace{-4em}\includegraphics[width=3.75in]{constant.png}\vspace{-2em}
  \caption{dfg}
\end{figure}

@@

Minstrel actually is better than SampleRate (except on short traces). Eit.

@@

\subsection{Availability}
We should make our github repo or something like that available here.
